Master's Research Proposal (DRAFT)

### 2024-06-28 proposal/Proposal.tex
small edit

\begin{enumerate}
\item \textbf{Isolating the Study of Movement.} In machine learning there is a well known phenomenon where features that are even mildly correlated with one another can compensate for one another in model fitting. A simple example would be something like height representing the "feature impact" of sex in a model of human health. Therefore it is always dubious to treat the relationship between a feature and a target as an actual indication of the true relationship. Within the spatial assessment paradigms in use today many different parameters of life history are fit together - movement, spatial heterogeneity in recruitment or mortality, fishing pressure, and so on. Because these are all fit as one model it is possible if not likely that features are "compensating" for one another and obscuring the actual relationships between the underlying processes and the outcomes. The simulation proposed herein fits movement on its own which should lead to a greater confidence in its representation of actual fish movement patterns. It also makes the debugging and improvement of those models much more clear and straightforward. 
\item \textbf{Generalized Strategy.} Individual based models (IBMs) also solve the problem mentioned above as they directly model movement as well. However IBMs are notoriously specific to the problem at hand. Furthermore most IBMs represent a specific hypothesis of behavior that has been coded up and as was mentioned in Section \ref{objective1} building models this way takes an enormous amount of time. The strategy proposed herein provides a generalized tool set for going from data, to a model, and then from there to a spatial simulation. And this means that researchers can contribute to building up a common tool set instead of having to start from ground zero each round.
\item \textbf{Repeated Usefulness.} There are obviously more straightforward ways to answer specific spatial questions than by using the framework proposed here. For example if trying to understand the value of a Marine Protected Area (MPA) one could simply study general abundances changes over the course of a year or apply more traditional tagging methodologies. The purpose of this framework would be to provide a centralized datastore, model, and simulation that could be used across many different problems.
\item \textbf{Interpretation and Communication.} Current standard spatial assessments depend on a movement matrix $X$ that defines how cohorts move between grids in the assessment at each time point. Such a matrix is ultimately an abstract mathematical concept that while useful in assessment makes the communication and interpretation of the underlying movement model difficult. Questions such as - what is driving the movement pattern seen - require actual parametrization of that movement matrix $X$. The strategy we are proposing provides this and therefore makes communication and feedback from stakeholders of the fishery far easier. Given engagement is such an important part of management this is paramount.  
\end{enumerate}

Obviously these each of these individual pros are not unique to the strategy proposed herein. IBMs, spatial assessment models, and more ad-hoc approaches all share some number of these advantages. However the strategy proposed herein presents an opportunity to gain all of these advantages at once which should make it a useful additional to the tools fisheries science already possesses. 
\newpage

\subsection{Spatial Management}

@@

\subsection{Spatial Assessments}

@@

\subsection{Modeling Movement}

>>>>

\begin{enumerate}
\item \textbf{Isolating the Study of Movement (\S \ref{spatial_assessments}).} In machine learning there is a well known phenomenon where features that are even mildly correlated with one another can compensate for one another in model fitting. A simple example would be something like height representing the "feature impact" of sex in a model of human health. Therefore it is always dubious to treat the relationship between a feature and a target as an actual indication of the true relationship. Within the spatial assessment paradigms in use today many different parameters of life history are fit together - movement, spatial heterogeneity in recruitment or mortality, fishing pressure, and so on. Because these are all fit as one model it is possible if not likely that features are "compensating" for one another and obscuring the actual relationships between the underlying processes and the outcomes. The simulation proposed herein fits movement on its own which should lead to a greater confidence in its representation of actual fish movement patterns. It also makes the debugging and improvement of those models much more clear and straightforward. 
\item \textbf{Generalized Strategy (\S \ref{modeling_movement}).} Individual based models (IBMs) also solve the problem mentioned above as they directly model movement as well. However IBMs are notoriously specific to the problem at hand. Furthermore most IBMs represent a specific hypothesis of behavior that has been coded up and as was mentioned in Section \ref{objective1} building models this way takes an enormous amount of time. The strategy proposed herein provides a generalized tool set for going from data, to a model, and then from there to a spatial simulation. And this means that researchers can contribute to building up a common tool set instead of having to start from ground zero each round.
\item \textbf{Repeated Usefulness.} There are obviously more straightforward ways to answer specific spatial questions than by using the framework proposed here. For example if trying to understand the value of a Marine Protected Area (MPA) one could simply study general abundances changes over the course of a year or apply more traditional tagging methodologies. The purpose of this framework would be to provide a centralized datastore, model, and simulation that could be used across many different problems.
\item \textbf{Interpretation and Communication (\S \ref{spatial_assessments}, \ref{spatial_management}).} Current standard spatial assessments depend on a movement matrix $X$ that defines how cohorts move between grids in the assessment at each time point. Such a matrix is ultimately an abstract mathematical concept that while useful in assessment makes the communication and interpretation of the underlying movement model difficult. Questions such as - what is driving the movement pattern seen - require actual parametrization of that movement matrix $X$. The strategy we are proposing provides this and therefore makes communication and feedback from stakeholders of the fishery far easier. Given engagement is such an important part of management this is paramount.  
\end{enumerate}

Obviously each of these individual pros are not unique to the strategy proposed herein. IBMs, spatial assessment models, and more ad-hoc approaches all share some number of these advantages. However the strategy proposed here presents an opportunity to gain all of these advantages at once which should make it a useful additional to the tools fisheries science already possesses. 
\newpage

\subsection{Spatial Management}\label{spatial_management}

@@

\subsection{Spatial Assessments}\label{spatial_assessments}

@@

\subsection{Modeling Movement}\label{modeling_movement}
